Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Discussing clone instance locations

\subsection{Clone instance location}
After mapping the relations between individual clones, we looked at the location of individual clone instances. A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, this claim is based on a very small dataset and a questionable way of measurement. We validated this claim over our corpus. For this, we chose the following categories:
\begin{enumerate}
  \item \textbf{Method Level:} A clone instance that does not exceed the boundaries of a single method (optionally including the declaration of the method itself).
  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class.
  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
\end{enumerate}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19.817           & 57,66               \\ \hline
Class Level        & 14.366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{center}
\end{table}

From these results we can see, somewhat surprisingly, that in our

>>>>

\subsection{Clone instance location}
After mapping the relations between individual clones, we looked at the location of individual clone instances. A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, this claim is based on a very small dataset and a questionable way of measurement. We validated this claim over our corpus. For this, we chose the following categories:
\begin{enumerate}
  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
\end{enumerate}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
Method Level       & 19.818           & 57,68               \\ \hline
Class Level        & 13.259           & 38,59               \\ \hline
Constructor Level  & 1.099            & 3,20                \\ \hline
Interface Level    & 110              & 0,32                \\ \hline
Enum Level         & 74               & 0,22                \\ \hline
\end{tabular}
\end{center}
\end{table}

From these results we can see, somewhat surprisingly, that the claim of 98\% of clones being produced at method-level is nowhere near correct. In fact, around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones is found in contructors. The amount of clones found in interfaces and enumerations is very low.
